---
title: "P8105 HW3"
author: "Yushan Wang"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
```

# Problem 1

```{r}
data("instacart")
```

The "instacart" dataset has `r ncol(instacart)` columns(variables) and `r nrow(instacart)` rows. 

The meaning of some of the key variables are listed below: (source: https://www.p8105.com/dataset_instacart.html)

`add_to_cart_order: order in which each product was added to cart`

`reordered: 1 if this prodcut has been ordered by this user in the past, 0 otherwise`

`eval_set: which evaluation set this order belongs in (Note that the data for use in this class is exclusively from the “train” eval_set)`

`order_number: the order sequence number for this user (1=first, n=nth)`

`order_dow: the day of the week on which the order was placed`

`order_hour_of_day: the hour of the day on which the order was placed`

`days_since_prior_order: days since the last order, capped at 30, NA if order_number=1`

The variables `eval_set`, `product_name`, `aisle`, and `department` are all characters. all other variables are intergers. 

The distribution summary of the variables of `add_to_cart_order`,`order_number`, `order_dow`, `order_hour_of_day`, `days_since_prior_order` are shown below:

```{r}
summary(instacart[c(3,7,8,9,10)])
```

**Count asiles and find most ordered aisles**

```{r}
instacart %>%
  count(aisle, name = "n_obs") %>% 
  arrange(desc(n_obs)) 

```

As shown in the counting table above, there are 134 aisles. Fresh vegetables is the aisles that most items ordered from.

**Plot of number of items ordered in each aisle**

```{r}
instacart %>%
  count(aisle, name = "n_obs") %>% 
  filter(n_obs > 10000) %>% 
  ggplot(aes(x = aisle, y = n_obs))+
  geom_point() +
  coord_flip() +
  ggtitle("") +
  xlab("aisle name") + ylab("number of items")
```

**Table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”**

```{r}
baking_ingredients = 
  instacart %>%
  filter(aisle == "baking ingredients") %>% 
  group_by(aisle, product_name) %>%
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) 

dog_food_care = 
  instacart %>%
  filter(aisle == "dog food care") %>% 
  group_by(aisle, product_name) %>%
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) 

packaged_vegetables_fruits = 
  instacart %>%
  filter(aisle == "packaged vegetables fruits") %>% 
  group_by(aisle, product_name) %>%
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) 

three_most_popular = 
  bind_rows(baking_ingredients[c(1,2,3),],dog_food_care[c(1,2,3),],packaged_vegetables_fruits[c(1,2,3),])

three_most_popular
```

**Table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered**

Table showing the mean hour of the day at which Pink Lady Apples are ordered

```{r}
Pink_Lady_Apples = 
  instacart %>% 
  filter(product_name == "Pink Lady Apples") %>% 
  group_by(order_dow) %>% 
  summarize(mean_hour_of_the_day = mean(order_hour_of_day))

```

Table showing the mean hour of the day at which Coffee Ice Cream are ordered
```{r}
Coffee_Ice_Cream = 
  instacart %>% 
  filter(product_name == "Coffee Ice Cream") %>% 
  group_by(order_dow) %>% 
  summarize(mean_hour_of_the_day = mean(order_hour_of_day))

```
Merge two tables

```{r}
meanhour_table = 
  merge(x = Pink_Lady_Apples, y = Coffee_Ice_Cream, by = "order_dow") %>%  
  rename(Pink_Lady_Apples_mean_hour = mean_hour_of_the_day.x, 
         Coffee_Ice_Cream_mean_hour = mean_hour_of_the_day.y)

```

Take mean of apple & ice cream mean hour

```{r}
meanhour_table %>% 
  mutate(mean_hour = (Pink_Lady_Apples_mean_hour+Coffee_Ice_Cream_mean_hour)/2 ) %>% 
  subset(select = c("order_dow", "mean_hour"))
```


## Problem 2

```{r, eval=FALSE}
data("brfss_smart2010")
```

## Problem 3

Load and tidy the data
```{r}
accel_df =
  read_csv("data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(day = factor(day))
```

There are 35 observations and 1443 variables in this dataset. The variables are `week`, `day_id`, `day`, and 1440 activity variables like `activity_1`, `activity_2`... to `activity_1440`. 

**Traditional analyses of accelerometer data**

```{r}
total_activity = 
  accel_df %>% 
  mutate(total_activity = sum(accel_df[4:1443])) %>% 
  subset(select = c("week","day_id","day","total_activity" ))

total_activity

```

The total activity in each day through five weeks are all the same.

**Make plot**

```{r}
accel_plot = 
  accel_df %>%
  pivot_longer(activity_1:activity_1440, names_to = "activity", values_to = "activity_count_per_minute") %>%
  ggplot(aes(x = day_id, y = activity_count_per_minute, colour = day_id)) +
  geom_point()
```

The graph shows that this person mainly had their activity count per minute below 2500.
